---
title: "Kubernetes Job Submission"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Kubernetes Job Submission}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(abba)
```

In support for Kubernetes, **abba** has several local submission functions to manage interface with a cluster. At a high level, these functions break down into three different categories:

- Submit a job
- Get job status
- Retrieve the log of the job

Functions specifically for interfacing with Kubernetes follow the naming convention `abba_k8s_*`, and more generally functions intended for local submission (i.e. not interface with the *abba* API) are suffixed with `_local()`. 

## Submit a Job
Job submission is handled by the function `abba_submit_k8s_job_local()`. This is the function used to submit a job on the API side.

```{r submit_job, eval=FALSE}
abba_submit_k8s_job_local(
  "/home/mike.stackhouse/repos/abba/test_programs/test_program.R",
  container = "atoruscontainers.azurecr.io/openval_4.2.1_focal:2023.09.0.02"
)
# job.batch/test-program-fbc3131d-a850-4081-8224-c06ef32821da created
# $job_id
# [1] "test-program-fbc3131d-a850-4081-8224-c06ef32821da"
# 
# $batch_id
# [1] "test_program-62e382a9-c1a7-4527-a32d-46600ee9ff80"
```

Note that this returns two fields: `job_id` and `batch_id`. The Job ID is the main field to consider and the identifier used downstream to interact with Kubernetes. Batch ID is a configurable identifier to group work within Kubernetes, and this is a placeholder for intended future functions that will help with the submission of several programs in a bundle.

## Get Job Status

Once the job is running in Kubernetes, **abba** can poll its status. This can be done using the function `abba_get_k8s_job_status_local()`

```{r get_status, eval=FALSE}
abba_get_k8s_job_status_local("test-program-fbc3131d-a850-4081-8224-c06ef32821da")
# $Succeeded
# $Succeeded$Jobs
# $Succeeded$Jobs[[1]]
# $Succeeded$Jobs[[1]]$id
# [1] "test-program-fbc3131d-a850-4081-8224-c06ef32821da-2dbr8"
# 
# $Succeeded$Jobs[[1]]$path
# [1] "/home/mike.stackhouse/repos/abba/test_programs/test_program.R"
# 
# 
# 
# $Succeeded$Description
# [1] "All containers in the Pod have terminated in success, and will not be restarted."
```

The job statuses can take on the following values:

| Status    | **Description**                                                                                                                                                                                                                                                          |
|-----------|--------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------------|
| Pending   | The Pod has been accepted by the Kubernetes cluster, but one or more of   the containers has not been set up and made ready to run. This includes time   a Pod spends waiting to be scheduled as well as the time spent downloading   container images over the network. |
| Running   | The Pod has been bound to a node, and all of the containers have been   created. At least one container is still running, or is in the process of   starting or restarting.                                                                                              |
| Succeeded | All containers in the Pod have terminated in success, and will not be   restarted.                                                                                                                                                                                       |
| Failed    | All containers in the Pod have terminated, and at least one container has   terminated in failure. That is, the container either exited with non-zero   status or was terminated by the system.                                                                          |
| Unknown   | For some reason the state of the Pod could not be obtained. This phase   typically occurs due to an error in communicating with the node where the Pod   should be running.                                                                                              |

The API interface methods will keep watching until they see a status other than "Pending" or "Running". "Succeeded", "Failed", or "Unknown" imply the job is "complete" in some watch. 

# Get the Log Content

In this context, the "log" refers to the stdout/stderr of the program itself. This returns into a list object with the Job ID and the individual lines written out by the program. Additionally, this could be some sort of failure in the pod. If the R program executes to completion, the content will contain all of the console output from the program itself. 

```{r watch_job, eval=FALSE}
abba_get_k8s_job_log_local("test-program-fbc3131d-a850-4081-8224-c06ef32821da")
# [[1]]
# [[1]]$job_id
# [1] "test-program-fbc3131d-a850-4081-8224-c06ef32821da"
# 
# [[1]]$log
# [1] "[1] 4"                   "Warning message:"        "This is a test warning " "La-di-da"                        
```

# Interacting with Kubernetes

Physical submission of work into Kubernetes is done using system calls to the `kubectl` utility. Note that for this to function, the calling user account (importantly, the user account executing the **abba** API), must have `kubectl` configured for the intended Kubernetes cluster. These local function will **not* work if `kubectl` is either not configured or not authorized. 
