---
title: "Workbench Job Submission"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Workbench Job Submission}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(abba)
```

In support for Workbench, **abba** has several local submission functions to manage interface with local Workbench cluster. At a high level, these functions break down into three different categories:

-   Submit a job
-   Get job status
-   Retrieve the log of the job

Functions specifically for interfacing with Workbench follow the naming convention `abba_rslauncher_*_local`.

## Submit a Job

Job submission is handled by the function `abba_rslauncher_submit_job_local()`. This is the function used to submit a job for a regular execution. To submit program for execution via logrx, `abba_rslauncher_submit_logrx_job_local` can be used.

```{r submit_job, eval=FALSE}
abba_rslauncher_submit_job_local(
  "/home/mike.stackhouse/repos/abba/test_programs/test_program.R"
  )
# [1] "TG9jYWw6bU9YcFMzeEZacVFaa1lLc2pRak1LZz09"
abba_rslauncher_submit_logrx_job_local(
  "/home/mike.stackhouse/repos/abba/test_programs/test_program.R"
  )
# [1] "TG9jYWw6VG5leWVvWFFseEN5M0JRVFptVjVIUT09"
```

Note that this returns a vector with job id and name being path of the program. The Job ID is the identifier used downstream to interact with Workbench.

By default, program log is physically saved in the program folder. The log destination is customizable via `log_path` keyword parameter.

## Get Job Status

Once the job is running in Workbench, **abba** can poll its status. This can be done using the function `abba_rslauncher_get_job_status_local()`

```{r get_status, eval=FALSE}
abba_rslauncher_get_job_status_local("TG9jYWw6bU9YcFMzeEZacVFaa1lLc2pRak1LZz09")
# TG9jYWw6bU9YcFMzeEZacVFaa1lLc2pRak1LZz09 
#                             "Finished" 
```

The job statuses can be "Running", and "Finished"(clarification needed).

# Get the Log Content

In this context, the "log" refers to the stdout/stderr of the program itself. This returns into a list object with the Job ID and the individual lines written out by the program. The content will contain all of the console output from the program itself.

```{r watch_job, eval=FALSE}
abba_rslauncher_get_job_log_local("TG9jYWw6bU9YcFMzeEZacVFaa1lLc2pRak1LZz09")
# [[1]]
# [1] "[1] 4"                   "Warning message:"        "This is a test warning " "La-di-da"                       
```
